Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-30 docs/00-manuscripts/ieee/tune-perc-sel-features.tex
update perc-sel-table

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Percentage of selected features of each fold during optimization for selected learners} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{rllrr}
  \toprule
 & Learner & Plot & Features (%) & RMSE \\ 
  \midrule
1 & \midrule\multirow{4}{*}{\textbf{RF Car}} & Laukiz1 & 0.00 & 27.48 \\ 
  2 &  & Oiartzun & 0.00 & 37.20 \\ 
  3 &  & Luiando & 0.00 & 36.98 \\ 
  4 &  & Laukiz2 & 0.03 & 15.39 \\ 
  5 & \midrule\multirow{4}{*}{\textbf{XGBoost Borda}} & Laukiz1 & 0.01 & 15.00 \\ 
  6 &  & Oiartzun & 0.68 & 36.15 \\ 
  7 &  & Luiando & 1.00 & 38.19 \\ 
  8 &  & Laukiz2 & 1.00 & 29.62 \\ 
  9 & \midrule\multirow{4}{*}{\textbf{SVM Relief}} & Laukiz1 & 0.00 & 35.50 \\ 
  10 &  & Oiartzun & 0.71 & 37.48 \\ 
  11 &  & Luiando & 0.71 & 14.89 \\ 
  12 &  & Laukiz2 & 0.95 & 37.19 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Percentage of selected features of each fold during optimization for selected learners} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrr}
  \toprule
Learner & Plot & Features (\%) & RMSE \\ 
  \midrule
\midrule\multirow{4}{*}{\textbf{RF Car}} & Laukiz1 & 0.00443 & 27.48 \\ 
   & Oiartzun & 0.00004 & 37.20 \\ 
   & Luiando & 0.00002 & 36.98 \\ 
   & Laukiz2 & 0.03037 & 15.39 \\ 
  \midrule\multirow{4}{*}{\textbf{XGBoost Borda}} & Laukiz1 & 0.00604 & 15.00 \\ 
   & Oiartzun & 0.68227 & 36.15 \\ 
   & Luiando & 0.99513 & 38.19 \\ 
   & Laukiz2 & 0.99976 & 29.62 \\ 
  \midrule\multirow{4}{*}{\textbf{SVM Relief}} & Laukiz1 & 0.00017 & 35.50 \\ 
   & Oiartzun & 0.71146 & 37.48 \\ 
   & Luiando & 0.70672 & 14.89 \\ 
   & Laukiz2 & 0.94696 & 37.19 \\ 
   \bottomrule
\end{tabular}
\end{table}
